Visualizations for article

### 2015-12-03 101-visualizations-for-article.Rmd
Rerun visualizations

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("stringr")
library("parallel")
library("scales")
library("textreuse")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract-date.R")
source("R/extract_code_names.R")
source("R/extract-state.R")
options("mc.cores" = 6L)
```

@@

```{r}
load("cache/corpus-lsh.rda")
codes <- c(scores$code_a, scores$code_b) %>% unique()
```

Calculate section matches and summarize them for a single code.

```{r}
CA1851 <- best_section_matches("CA1851", scores, threshold = 0.15)
CA1851
summarize_borrowings(CA1851)
```

Apply that to all the codes.

```{r}
code_match_summary <- codes %>% 
  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
code_match_summary
```

@@

```{r}
edges_pct <-
  code_match_summary %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         borrower_date >= match_date) %>% 
  select(borrower_code, match_code, weight = percentage_sections) %>% 
  group_by(borrower_code) %>% 
  top_n(2, weight)
edges_pct

@@

for (i in seq(1850, 1900, 5)) {
  png(filename = paste0("out/field-code-network-ALL", i, ".png"), width = 1200,
      height = 900)
  plot_before_year(g, i)
  dev.off()
}
```

@@

```{r}
minimum_n <- 20
top_matches <- 3
codes_not_to_plot <- c(
  # "CO868", 
#   "CT1879", 
  # "FL1847", 
  # "FL1892", 
  "GA1851",
  "GA1860", 
  "HI1859", 
  "HI1897", 
  # "IL1866", 
  "LA1825", 
  "LA1844", 
#   "MS1848", 
#   "MS1857", 
  # "NY1876", 
  # "NY1879",
  # "VA1860", 
  "VA1893", 
  "WV1868" 
  )
# codes_not_to_plot <- NULL

edges_n <- code_match_summary %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code)) %>% 
  filter(!is.na(match_code),
         borrower_date >= match_date,
         n >= minimum_n) %>%  
  select(borrower_code, match_code, weight = n) %>% 
  group_by(borrower_code) %>% 
  top_n(top_matches, weight) %>% 
  ungroup() %>% 
  mutate(weight = rescale(weight)) %>% 
  filter(!borrower_code %in% codes_not_to_plot,
         !match_code %in% codes_not_to_plot)
edges_n

@@

```{r}
min_state_borrowings <- 100
top_matches <- 3
edges_states <- code_match_summary %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code),
         borrower_state = extract_state(borrower_code),
         match_state = extract_state(match_code)) %>% 
  filter(!is.na(match_code),
         borrower_date >= match_date,
         borrower_state != match_state) %>% 
  group_by(borrower_state, match_state) %>% 
  summarize(n = sum(n)) %>% 
  filter(n >= min_state_borrowings) %>% 
  select(borrower_state, match_state, weight = n) %>% 
  group_by(borrower_state) %>% 
  top_n(top_matches, weight) %>% 
  ungroup() %>% 
  mutate(weight = rescale(weight))

>>>>

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("stringr")
library("scales")
library("textreuse")
source("R/helper.R")
source("R/section-matches.R")
```

@@

```{r}
load("cache/corpus-lsh.rda")
```

@@

```{r}
edges_pct <- summary_matches %>% 
  filter(percent_borrowed >= 0.05,
         !is.na(match_code)) %>% 
  select(borrower_code, match_code, weight = percent_borrowed) %>% 
  group_by(borrower_code) %>% 
  top_n(2, weight)
edges_pct

@@

for (i in seq(1850, 1900, 5)) {
  plot_before_year(g, i)
}
```

@@

```{r}
minimum_n <- 20
top_matches <- 2
codes_not_to_plot <- c(
  # "CO868", 
  # "CT1879", 
  # "FL1847", 
  # "FL1892", 
  "GA1851",
  "GA1860", 
  "HI1859", 
  "HI1897",
  # "IL1866", 
  "LA1825", 
  "LA1844" 
#   "MS1848", 
#   "MS1857", 
  # "NY1876", 
  # "NY1879",
  # "VA1860", 
  # "VA1893", 
  # "WV1868" 
  )
# codes_not_to_plot <- NULL

edges_n <- summary_matches %>% 
  filter(!is.na(match_code),
         sections_borrowed >= minimum_n) %>%  
  select(borrower_code, match_code, weight = sections_borrowed) %>% 
  group_by(borrower_code) %>% 
  top_n(top_matches, weight) %>% 
  ungroup() %>% 
  mutate(weight = rescale(weight)) %>% 
  filter(!borrower_code %in% codes_not_to_plot,
         !match_code %in% codes_not_to_plot)
edges_n

@@

```{r}
min_state_borrowings <- 100
top_matches <- 2
edges_states <- summary_matches %>% 
  mutate(borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code),
         borrower_state = extract_state(borrower_code),
         match_state = extract_state(match_code)) %>% 
  filter(!is.na(match_code),
         borrower_date >= match_date,
         borrower_state != match_state) %>% 
  group_by(borrower_state, match_state) %>% 
  summarize(n = sum(sections_borrowed)) %>% 
  filter(n >= min_state_borrowings) %>% 
  select(borrower_state, match_state, weight = n) %>% 
  group_by(borrower_state) %>% 
  top_n(top_matches, weight) %>% 
  ungroup() %>% 
  mutate(weight = rescale(weight))
